|

### 2023-05-11 paper/03-methods.Rmd
small fix to fixed effects

To this end, we fit a multilevel model to evaluate pass rushers' impact on the average STRAIN observed in a play, while accounting for their pass blocker, QB, and play-level information.
We identify the pass blocker linked with the pass rusher of interest using the data provided by PFF.
Since there can be multiple blockers linked to a rusher, for simplicity we only consider the nearest blocker positioned to the pass rusher at the start of the play.
We use random intercepts for the three player groups: (1) pass rushers as $R$, (2) nearest pass blockers as $B$, and (3) QBs as $Q$.
The coefficients $\beta$ for additional information $X_{ij}$ about pass rusher $j$ in play $i$ are estimated as fixed-effects. 
Our model for the average STRAIN by pass rusher $j$ on play $i$ is as follows.
\begin{equation}
\begin{aligned}
\overline{\text{STRAIN}}_{ij} &\sim N(R_{r[ij]} + B_{b[ij]} + Q_{q[i]} + X_{ij} \cdot \beta, \sigma^2), \text{ for } i = 1, \dots, n \text{ plays} \\
R_{r} &\sim N(\mu_R, \sigma^2_R), \text{ for } r = 1, \cdots, \text{ \# of pass rushers}, \\
B_{b} &\sim N(\mu_B, \sigma^2_B), \text{ for } b = 1, \cdots, \text{ \# of pass blockers}, \\
Q_{q} &\sim N(\mu_Q, \sigma^2_Q), \text{ for } q = 1, \cdots, \text{ \# of QBs}.
\end{aligned}
\end{equation}

>>>>

To this end, we fit a multilevel model to evaluate pass rushers' impact on the average STRAIN observed in a play, while accounting for their pass blocker, QB, and play-level attributes.
We identify the pass blocker linked with the pass rusher of interest using the data provided by PFF.
Since there can be multiple blockers linked to a rusher, for simplicity, we consider the nearest blocker positioned to the pass rusher at the start of the play.
We use random intercepts for the three player groups: (1) pass rushers as $R$, (2) nearest pass blockers as $B$, and (3) QBs as $Q$.
The coefficients $\beta$ for additional information $X_{ij}$ about pass rusher $j$ in play $i$ are estimated as fixed-effects. 
Our model for the average STRAIN by pass rusher $j$ on play $i$ is as follows.
\begin{equation}
\begin{aligned}
\overline{\text{STRAIN}}_{ij} &\sim N(R_{r[ij]} + B_{b[ij]} + Q_{q[i]} + X_{ij} \cdot \beta, \sigma^2), \text{ for } i = 1, \dots, n \text{ plays} \\
R_{r} &\sim N(\mu_R, \sigma^2_R), \text{ for } r = 1, \cdots, \text{ \# of pass rushers}, \\
B_{b} &\sim N(\mu_B, \sigma^2_B), \text{ for } b = 1, \cdots, \text{ \# of pass blockers}, \\
Q_{q} &\sim N(\mu_Q, \sigma^2_Q), \text{ for } q = 1, \cdots, \text{ \# of QBs}.
\end{aligned}
\end{equation}

### 2023-05-11 paper/04-results.Rmd
small fix to fixed effects

\begin{table}
\caption{Fixed-effects coefficients estimates for the multilevel model for average STRAIN. Note that the reference pass rusher level is defensive end (DE), denoted PR:DE; and the reference pass blocker level is tackle (T), denoted PB:T. \label{tab:fixedeff}}
\centering
\begin{tabular}{lrrrr}
\hline
& estimate & se & $t$-statistic & $p$-value \\ 
\hline
Intercept & 0.378 & 0.009 & 43.310 & 0.000 \\ 
Length of play & -0.004 & 0.000 & -38.214 & 0.000 \\
Number of blockers & -0.064 & 0.003 & -24.788 & 0.000 \\
$I_{\text{\{PR:DT\}}}$ & -0.081 & 0.008 & -10.340 & 0.000 \\
$I_{\text{\{PR:interior\}}}$ & 0.058 & 0.011 & 5.332 & 0.000 \\
$I_{\text{\{PR:NT\}}}$ & -0.106 & 0.012 & -9.174 & 0.000 \\
$I_{\text{\{PR:OLB\}}}$ & 0.062 & 0.008 & 7.695 & 0.000 \\
$I_{\text{\{PR:secondary\}}}$ & 0.145 & 0.012 & 12.328 & 0.000 \\
$I_{\text{\{PB:C\}}}$ & -0.023 & 0.006 & -3.625 & 0.000 \\
$I_{\text{\{PB:G\}}}$ & -0.011 & 0.005 & -2.290 & 0.023 \\ 
$I_{\text{\{PB:other\}}}$ & -0.013 & 0.007 & -1.911 & 0.056 \\
\hline
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{Fixed-effects coefficients estimates for the multilevel model for average STRAIN. Note that the reference pass rusher level is defensive end (DE), denoted R:DE; and the reference pass blocker level is tackle (T), denoted B:T. \label{tab:fixedeff}}
\centering
\begin{tabular}{lrrrr}
\hline
& estimate & se & $t$-statistic & $p$-value \\ 
\hline
Intercept & 0.378 & 0.009 & 43.310 & 0.000 \\ 
Length of play & -0.004 & 0.000 & -38.214 & 0.000 \\
Number of blockers & -0.064 & 0.003 & -24.788 & 0.000 \\
$I_{\text{\{R:DT\}}}$ & -0.081 & 0.008 & -10.340 & 0.000 \\
$I_{\text{\{R:interior\}}}$ & 0.058 & 0.011 & 5.332 & 0.000 \\
$I_{\text{\{R:NT\}}}$ & -0.106 & 0.012 & -9.174 & 0.000 \\
$I_{\text{\{R:OLB\}}}$ & 0.062 & 0.008 & 7.695 & 0.000 \\
$I_{\text{\{R:secondary\}}}$ & 0.145 & 0.012 & 12.328 & 0.000 \\
$I_{\text{\{B:C\}}}$ & -0.023 & 0.006 & -3.625 & 0.000 \\
$I_{\text{\{B:G\}}}$ & -0.011 & 0.005 & -2.290 & 0.023 \\ 
$I_{\text{\{B:other\}}}$ & -0.013 & 0.007 & -1.911 & 0.056 \\
\hline
\end{tabular}
\end{table}
